Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Add ZIP code
Estimator for predicting --> predictor

% Affiliations / Addresses (Add [1] after \address if there is only one
% affiliation.)
\address[1]{%
 Center for Ocean Renewable Energy, University of New Hampshire, 24
Colovos Rd., \mbox{Durham, NH \hl{zip code}, USA}}

@@

% Abstract (Less than 200 words)
\abstract{Experiments were performed with a large laboratory-scale high solidity
 cross-flow turbine to investigate Reynolds number effects on performance and
 wake characteristics and to establish scale thresholds for physical and
 numerical modeling of individual devices and arrays.~It was demonstrated that
 the performance of the cross-flow turbine becomes essentially $Re$-independent
 at a Reynolds number based on a turbine diameter of $Re_D \approx 10^6$ or an
 approximate average Reynolds number based on a blade chord of $Re_c \approx 2
 \times 10^5$.~A simple model that calculates the peak torque coefficient from static
 foil data and cross-flow turbine kinematics was shown to be a reasonable
 estimator for predicting the Reynolds number dependence of an actual cross-flow
 turbine operating under dynamic conditions. Mean velocity and turbulence
 measurements in the near-wake showed subtle differences over the range of $Re$
 investigated.~However, when transport terms for the streamwise momentum and mean
 kinetic energy were calculated, a similar $Re$ threshold was revealed. These
 results imply that physical model studies of cross-flow turbines should achieve
 $Re_D \sim 10^6$ to properly approximate both the performance and wake dynamics
 of full-scale devices and arrays.}

>>>>

% Affiliations / Addresses (Add [1] after \address if there is only one
% affiliation.)
\address[1]{%
 Center for Ocean Renewable Energy, University of New Hampshire, 24
Colovos Rd., \mbox{Durham, NH 03824, USA}}

@@

% Abstract (Less than 200 words)
\abstract{Experiments were performed with a large laboratory-scale high solidity
 cross-flow turbine to investigate Reynolds number effects on performance and
 wake characteristics and to establish scale thresholds for physical and
 numerical modeling of individual devices and arrays.~It was demonstrated that
 the performance of the cross-flow turbine becomes essentially $Re$-independent
 at a Reynolds number based on a turbine diameter of $Re_D \approx 10^6$ or an
 approximate average Reynolds number based on a blade chord of $Re_c \approx 2
 \times 10^5$.~A simple model that calculates the peak torque coefficient from static
 foil data and cross-flow turbine kinematics was shown to be a reasonable
 predictor for Reynolds number dependence of an actual cross-flow
 turbine operating under dynamic conditions. Mean velocity and turbulence
 measurements in the near-wake showed subtle differences over the range of $Re$
 investigated.~However, when transport terms for the streamwise momentum and mean
 kinetic energy were calculated, a similar $Re$ threshold was revealed. These
 results imply that physical model studies of cross-flow turbines should achieve
 $Re_D \sim 10^6$ to properly approximate both the performance and wake dynamics
 of full-scale devices and arrays.}
